---
output: github_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "vignettes/readme_figs/")
```

# `OPColors` intro 

`OPColors` contains a selection of `ggplot2` color palettes that I like (or can at least tolerate to some degree)

## Installation


Install `OPColors` from GitHub:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("jaredhuling/OPColors")
```

Access the `OPColors` color palettes with `OPColors()`:

```{r eval = TRUE, message = FALSE, warning = FALSE}
devtools::install_github("cromer043/OPColors")

library(OPColors)

```

## Display all available palettes

### Discrete palettes
```{r displayall, fig.height = 8}
display_all_OPColors()
```


# Discrete Color Palettes

## Use with `ggplot2`

Now use `scale_color_OPColors()` with `ggplot2`:

```{r eval = TRUE, message = FALSE, warning = FALSE}
library(ggplot2)
library(gridExtra)

data(morley)

pltl <- ggplot(data = morley, aes(x = Run, y = Speed,
group = factor(Expt),
colour = factor(Expt))) +
    geom_line(size = 2) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey97"),
          panel.border = element_blank(),
          legend.position = "bottom")

pltd <- ggplot(data = morley, aes(x = Run, y = Speed,
group = factor(Expt),
colour = factor(Expt))) +
    geom_line(size = 2) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "grey15"),
          legend.key = element_rect(fill = "grey15"),
          panel.border = element_blank(),
          panel.grid.major = element_line(color = "grey45"),
          panel.grid.minor = element_line(color = "grey25"),
          legend.position = "bottom")

grid.arrange(pltl + scale_color_OPColors(palette = "Default"),
             pltd + scale_color_OPColors(palette = "Primary"), ncol = 2)

grid.arrange(pltl + scale_color_OPColors(palette = "Brilliant Baby default"),
             pltd + scale_color_OPColors(palette = "Brilliant Baby primary"), ncol = 2)



```

Color palettes can be displayed using `display_OPColors()`

## default
```{r}
display_OPColors("Default")
```

## Primary
```{r}
display_OPColors("Primary")
```

## Brilliant Baby default
```{r}
display_OPColors("Brilliant Baby default")
```

## Brilliant Baby primary
```{r}
display_OPColors("Brilliant Baby primary")
```

## College Access default
```{r}
display_OPColors("College Access default")
```

## College Access primary
```{r}
display_OPColors("College Access primary")
```

## College Completion default
```{r}
display_OPColors("College Completion default")
```

## College Completion primary 
```{r}
display_OPColors("College Completion primary")
```

## Kindergarden to College default
```{r}
display_OPColors("K2C default")
```

## Kindergarden to College primary
```{r}
display_OPColors("K2C primary")
```


